%-------------------------
% Resume in LaTeX
% Author: Nikhil Badyal
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\footskip}{0.5in}
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.nikhilbadyal.com/}{\Large Nikhil Badyal}} &  \href{mailto:possum-dawn-engulf@duck.com}{possum-dawn-engulf@duck.com} \\
  Remote, India & \href{https://github.com/nikhilbadyal}{github.com/nikhilbadyal} \\
  \href{https://www.nikhilbadyal.com/}{nikhilbadyal.com} & \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}\label{sec:summary}
  \resumeSubHeadingListStart
    \resumeSubItem{Senior Software Engineer with 3+ years of experience}
    {Specialized in building scalable backend systems, multi-tenant SaaS architecture, and cloud infrastructure. Proven expertise in API development, ETL pipelines, DevOps, and Elasticsearch. Strong
    open-source contributor with a focus on performance, reliability, and automation. Delivered solutions that improved system performance by \textbf{90\%} and reduced costs by \textbf{35\%}.}
  \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}\label{sec:education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Jadavpur University}{Kolkata, India}
    {Bachelor of Engineering in Computer Science and Engineering; GPA: 8.5}{July 2018 -- July 2022}
      \resumeItemListStart
        \resumeItem{Relevant Coursework}{Data Structures, Algorithms, Database Systems, Distributed Computing}
        \resumeItem{Honors}{Graduated with Distinction}
      \resumeItemListEnd
    \resumeSubheading
      {Jawahar Navodaya Vidyalaya}{JandK, India}
      {Senior Secondary; Percentage: 95\%}{Nov 2011 -- June 2018}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}\label{sec:experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Anchanto}{Remote, India}
    {Senior Software Engineer}{Feb 2024 -- Present}
    \resumeItemListStart
      \resumeItem{Multi-Tenant Architecture Lead}
        {Architected and led the successful migration from a single-tenant to a multi-tenant SaaS platform, supporting \textbf{100+ customers} and achieving a \textbf{~35\% reduction} in infrastructure
        costs. Improved system scalability and reliability, reducing downtime by \textbf{50\%}.}
      \resumeItem{Tooling Development}
        {Developed \textbf{EsXport}, an open-source tool for complex Elasticsearch data extraction, decreasing export times by \textbf{90\%}.}
      \resumeItem{Feature Development}
        {Engineered the whitelabeled branded URL feature, empowering clients with custom domains for public searches and enhancing brand identity, leading to a \textbf{20\% increase} in customer
        satisfaction.}
      \resumeItem{Centralized Logging System}
        {Implemented and managed a robust logging pipeline using the ELK stack, ingesting over \textbf{600GB} of daily production server logs for real-time monitoring, analysis, and accelerated issue
        resolution. Reduced mean time to resolution (MTTR) by \textbf{40\%}.}
    \resumeItemListEnd

  \resumeSubheading
    {Anchanto}{Remote, India}
    {Software Engineer}{May 2022 -- Feb 2024}
    \resumeItemListStart
      \resumeItem{API Development}
        {Developed and optimized \textbf{50+} APIs handling \textbf{20M+} daily requests, managing \textbf{100M+} parcels and \textbf{5B+} events to support seamless platform operations. Maintained \textbf{90\%+} test coverage by writing robust unit and integration test cases.}
      \resumeItem{System Designer}
        {Designed the database schema and architecture for efficient data storage, including table designs, ensuring high-performance event tracking and real-time search across millions of parcels.}
      \resumeItem{ETL Engineer}
        {Built ETL pipelines to transform raw tracking data from \textbf{100+} external carriers into manageable formats, enabling seamless integration, efficient data storage, and improved parcel tracking. These pipelines processed over 5 billion records, ensuring that the data was optimized for platform performance and usability.}
      \resumeItem{Cloud Infrastructure Engineer}
        {Managed the complete cloud infrastructure, overseeing server uptime, downtimes, deployments and ensuring smooth and reliable operations while reducing costs by \textbf{30\%}. I also ensured adherence to the \textbf{99.9999\%} SLA commitment, maintaining exceptional service reliability.}
      \resumeItem{Data Tooling Engineer}
        {Wrote \textbf{Esyncer}, a tool to synchronize data from SQL (Postgres) to No SQL (Elasticsearch), enabling faster search capabilities.}
      \resumeItem{Performance Engineer}
        {Optimized search capabilities to enable lightning-fast querying and tracking of 100 million parcels and 5B events in \textbf{2 ms}, down from \textbf{30 sec}. Integrated Elasticsearch with a replication setup, ensuring high availability and performance for real-time searches.}
      \resumeItem{DevOps Engineer}
        {Dockerized the infrastructure, enhancing consistency and scalability across environments. Reduced setup time from 3-4 days to just a few hours by streamlining the process to a simple Docker installation.}      \resumeItemListEnd
  \resumeSubheading
        {Anchanto}{Remote, India}
        {Software Engineering Intern}{Jan 2022 -- May 2024}
      \resumeItemListStart
      \resumeItem{Backend \& ETL Engineer}
        {Developed and wrote \textbf{10+} APIs to power core platform functionalities and improve system performance, while managing over \textbf{10M} parcels and \textbf{100M} events through SQL-based transformation scripts for seamless data flow.}
      \resumeItem{CI/CD Pipeline Setup and Automation}
        {Set up and configured CI/CD pipelines to automate the build, test, and deployment processes, significantly streamlining development workflows. Transitioned from manual SSH deployments to fully automated deployments across Dev, QA, and Production environments. This shift reduced deployment time from a full day to just minutes, minimized downtime, and ensured consistent and reliable delivery cycles, improving overall code quality and accelerating release timelines.}      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------AWARDS AND RECOGNITION-----------------
\section{Awards and Recognition}\label{sec:awards-and-recognition}
  \resumeSubHeadingListStart
    \resumeSubItem{Anchanto Innovation Challenge Winner – Operational Efficiency (2024)}
      {Recognized for building a \textbf{low-code integration engine} that significantly accelerated the development of carrier integrations. By using JSON-based configurations to define data sources,
       processing rules, and destinations, we eliminated repetitive coding and achieved faster deployment cycles, improving integration time-to-market and operational scalability.}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}\label{sec:projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Esxport}
      {Open-source tool to export Elasticsearch indices. \href{https://github.com/nikhilbadyal/esxport}{[GitHub]}}
    \resumeSubItem{Tg-TOTP}
      {Telegram bot for generating 2FA tokens for secure logins. \href{https://github.com/nikhilbadyal/tg-totp}{[GitHub]}}
    \resumeSubItem{Ghaction-rm-release}
      {GitHub action for automating release cleanups with tag removal. \href{https://github.com/nikhilbadyal/ghaction-rm-releases}{[GitHub]}}
    \resumeSubItem{KeepNotes}
      {Cross-platform note-taking app built with Flutter. \href{https://github.com/nikhilbadyal/keepnotes}{[GitHub]}}
    \resumeSubItem{Pgextras}
      {Unofficial Heroku Pgextras port for PostgreSQL instance statistics. \href{https://github.com/nikhilbadyal/pgextras}{[GitHub]}}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}\label{sec:programming-skills}
  \begin{tabularx}{\textwidth}{X X}
    \textbf{Languages:} Python, C++, SQL, Dart & \textbf{Databases:} PostgreSQL, Redis, Elasticsearch \\
    \textbf{Frameworks:} Django, Flutter & \textbf{DevOps:} Docker, Git \\
    \textbf{Cloud:} AWS & \textbf{Tools:} Kibana, Logstash \\
  \end{tabularx}

%-------------------------------------------
\end{document}
